Helixer: Cross-species Gene Annotation Of Large Eucaryotic Genomes Using Deep Learning

### 2020-04-25 paper/main.tex
some results text

Our models, however, tend to perform less well for the very smallest and largest genomes or species that are phylogenetically the furthest away from our training genomes. This is the case for both animals and plants and is visualized by the Supplemental Figures S?-?. We do not, for example, consistently predict very well on the algae as well as the non-avian reptiles. While one of the the algaes were included in our training genomes, the non-avian reptiles were not represented.

AUGUSTUS does outperform us rather consistently on the smallest genomes, but struggles much more the larger the genomes get. The difference in prediction quality is especially strong for mammals and the largest plants.

@@

>>>>

Our models, however, tend to perform less well for the very smallest and largest genomes or species that are phylogenetically the furthest away from our training genomes. This is the case for both animals and plants and is visualized by the Supplemental Figures S?-?. We do not, for example, consistently predict very well on the algae as well as the non-avian reptiles. While one of the the algae were included in our training genomes, the non-avian reptiles were not. Our model also tends to show higher uncertainty around transitions of annotation classes (e.g. from UTR to CDS) due to the lack of further post-processing of the basepair wise predictions.

AUGUSTUS does outperform us rather consistently on the smallest genomes, but struggles much more the larger the genomes get. The difference in prediction quality is especially strong for mammals, which tend to have large genomes with very long genes, and the largest plants.

@@

Different set of training genomes could lead to a shift in strengths and weaknesses of the model while a larger and more spread out set of high quality genomes could result in a wider range of genomes with decent predictions.
